---
title: "Covid in Jails- Weekly Report" 
date: "`r Sys.Date()`"
output: 
  word_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r message=FALSE, warning=FALSE, include=FALSE}
# Libraries
library(tidyverse)
library(RCurl)
library(lubridate)
library(kableExtra)
library(knitr)

# API Pull
enrollment_data_raw <- postForm(
  uri='https://redcap.stanford.edu/api/',
  token='02528A04B2AEA71673CE1858FBA6D2BC',
  content='report',
  format='csv',
  report_id='73260',
  csvDelimiter='',
  rawOrLabel='raw',
  rawOrLabelHeaders='raw',
  exportCheckboxLabel='false',
  returnFormat='csv'
)

qc_data_raw <- postForm(
  uri='https://redcap.stanford.edu/api/',
  token='02528A04B2AEA71673CE1858FBA6D2BC',
  content='report',
  format='csv',
  report_id='78082',
  csvDelimiter='',
  rawOrLabel='raw',
  rawOrLabelHeaders='raw',
  exportCheckboxLabel='false',
  returnFormat='csv'
)

# Read in data 
enrollment_data <-  
  read_csv(enrollment_data_raw) 


qc_data <- 
  read_csv(qc_data_raw) %>% 
  filter(!is.na(quality_control_comments_complete))

data <- 
  enrollment_data %>% 
  left_join(qc_data, by = c("barcode_id", "redcap_event_name")) %>% 
  filter(redcap_event_name != "quality_control_arm_1")

data %>% 
  count(redcap_event_name)

#glimpse(enrollment_data)

#===============================================================================

# Code
```

```{r, echo=FALSE, warning=FALSE}
enrollment_data_cleaned <- 
  data %>% 
  mutate(
    population = case_when(
      consent_stf_or_incarc == 1 ~ "staff",
      consent_stf_or_incarc == 2 ~ "incarcerated",
      TRUE ~ as.character(consent_stf_or_incarc)
                           ),
   pop2 = case_when(
      str_detect(barcode_id, "-S-") == TRUE ~ "staff",
      str_detect(barcode_id, "-I-") == TRUE ~ "incarcerated",
      TRUE ~ "test"
                           ),
   followup_count = 
     ifelse(str_detect(redcap_event_name, "3") == TRUE, 1, 0), 
   baseline_count = 
     ifelse(str_detect(redcap_event_name, "baseline") == TRUE & consent_yn == 1, 1, 0),
    consent = consent_yn,
    consent_timestamp = as_datetime(consent_timestamp),
    enrollment_week = floor_date(results_date, "week"), 
    followup_1_week = floor_date(results_date, "week"),
    this_week = if_else(results_date >= today() - days(6), 1, 0), 
   followup_week = 
     ifelse(str_detect(redcap_event_name, "3") == TRUE & this_week == 1, 1, 0), 
   baseline_week = 
     ifelse(
       str_detect(redcap_event_name, "baseline") == TRUE &
         consent_yn == 1 &
         this_week == 1,
       1,
       0
       ),
  ) 

```

```{r, echo=FALSE, warning=FALSE}
# ### Total Enrolled
# enrollment_data_cleaned %>% 
#   filter(consent_yn == 1) %>% 
#   count(population) %>% 
#   knitr::kable("markdown")
```

```{r, echo=FALSE, warning=FALSE}
# ### Enrolled this week
# enrollment_data_cleaned %>% 
#   filter(consent_yn == 1, enrollment_week >= today() - days(7)) %>% 
#   count(population) %>% 
#   knitr::kable("markdown")
```

## Project Enrollments

```{r, echo=FALSE, warning=FALSE}
enrollment_data_cleaned %>%
filter(pop2 != "test") %>%
group_by(pop2) %>%
summarise(
  `Weekly Enrollments` = sum(baseline_week, na.rm = TRUE), 
  `Follow ups` = sum(followup_week, na.rm = TRUE),
  `Total Enrolled` = sum(baseline_count, na.rm = TRUE)
) %>% 
  rename(Population = pop2) %>% 
   knitr::kable("markdown")

```


### Enrollment over time
```{r, echo=FALSE}

enrollment_data_cleaned %>% 
  filter(consent_yn == 1,this_week == 1) %>% 
  select(population, results_date) %>% 
  #filter(population == "incarcerated") %>% 
  #select(barcode_id,results_date)
  ggplot() +
  geom_bar(aes(x = results_date)) + 
  scale_x_date(date_breaks = "day", date_labels = "%A") +
  theme(legend.position = "top") +
  labs(
    title = "Enrollments This Week",
    y = "Number of Participants Enrolled", 
    x = "Day of week"
    #source = str_glue("Updated", {today())
  )

enrollment_data_cleaned %>% 
  filter(consent_yn == 1) %>% 
  ggplot(aes(fill = population, x = enrollment_week)) +
  geom_bar(position = "stack") + 
  scale_x_date(date_breaks = "month", date_labels = "%b") +
  theme(legend.position = "top") +
  labs(
    title = "Enrollments into COVID in Local Jails Project over time",
    y = "Number of Participants Enrolled by Week", 
    x = "Month"
    #source = str_glue("Updated", {today())
  )


```

## Accomplishments for the week 
- Continued interest from incarcerated populations 
- Spent time in San Mateo Facilities this week 

## Challenges 

- Limited days of testing 
- At&T payment needed 
- Lockdown on Wednesday prevented testing 
       


## Quality Control Issues 


```{r, echo=FALSE}
#glimpse(enrollment_data_cleaned)
enrollment_data_cleaned %>%
filter(consent_yn == 1) %>%
mutate(
  this_week = if_else(enrollment_week >= today() - days(7), 1, 0)
) %>% 
group_by(population) %>% 
summarise(
  "Resolved QC Issues" = sum(qc_status == 1, na.rm = TRUE), 
  "Open QC Issues" = sum(qc_status == 2, na.rm = TRUE),
  "QC Issues for Discussion" = sum(qc_status == 3, na.rm = TRUE),
  ) %>% 
knitr::kable("markdown", align = "c")



```

### Types of QC Issues 
The QC issues we have are as follows 

##### Issues for Discussion Amongst the team
```{r, echo=FALSE}

#QC Items for discussion 
enrollment_data_cleaned %>%
filter(consent_yn == 1, qc_status == 3) %>%
pull(qc_notes)


```
##### Other QC Issues
```{r, echo=FALSE}

#QC Items for discussion 
enrollment_data_cleaned %>%
filter(qc_status == 2) %>%
count(qc_notes) %>% 
  knitr::kable("markdown", align = "c")
  

```






